Modelling BCG vaccination in the UK

### 2019-08-06 rmds/02-background.Rmd
table formatting

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note the high percentage of TB cases with HIV in sub-saharan Africa. The percentages of HIV in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR"}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Note that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. The percentages of rifampicin resistances in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR (see \\@ref(getTBinR) for details)"}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

```{r prop-rr-with-mdr-tab, warning = FALSE}
summarise_tb_burden(countries = "Russia", 
                    metric = "e_mdr_pct_rr_new", verbose = FALSE,
                    year = 2017, stat = "median") %>% 
  mutate_at(.vars = c("e_mdr_pct_rr_new", "e_mdr_pct_rr_new_lo", "e_mdr_pct_rr_new_hi"),
            funs(ifelse(. > 100, 100, .))) %>% 
  arrange(desc(area)) %>% 
  mutate(`Median percentage of RR* cases with MDR** (95% IQR***)` = 
           pretty_ci(e_mdr_pct_rr_new,
                     e_mdr_pct_rr_new_lo, 
                     e_mdr_pct_rr_new_hi, digits = 1)) %>% 
  mutate(`Median Proportion of RR* cases with MDR** (95% IQR***)` = 
           ifelse(area == "Russian Federation", paste(pretty_round(e_mdr_pct_rr_new), "***"),
                  as.character(`Median percentage of RR* cases with MDR** (95% IQR***)`)
                  )) %>% 
  select(Area = area, `Median percentage of RR* cases with MDR** (95% IQR***)`) %>% 
  knitr::kable(
               caption = "Percentage (\\%) of rifampicin resistant TB cases that have multi-drug resistant TB in Russia and regional medians, with interquartile ranges.",
        booktabs = TRUE) %>% 
  add_footnote(label = c("* Rifampicin resistance", "** Multi-Drug Resistant TB", "*** Interquartile Range"), notation = "none") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  {.}
```

@@

TB incidence in England and Wales has decreased dramatically from a century ago (Figure \@ref(fig:plot-incidence)^[or see http://www.seabbs.co.uk/shiny/TB_England_Wales]) for an interactive dashboard). However, in the past several decades, incidence rates first stabilised and have since increased since their lowest point in the 1990s. In 2000, there were 6044 notified TB cases in England, increasing to a maximum of 8280 notified TB cases in 2011. Since then, notifications have declined year-on-year.[@PHE2016a] Figure \@ref(fig:plot-incidence) includes the interventions discussed above (Table \@ref(tab:tab-interventions)) and indicates that the introduction of several antibiotics and BCG vaccination in the 1950s may have led to an extended decrease in incidence.

>>>>

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note the high percentage of TB cases with HIV in sub-saharan Africa. The percentages of HIV in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.height = 4}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Note that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. The percentages of rifampicin resistances in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR (see \\@ref(getTBinR) for details)", fig.height = 4}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

```{r prop-rr-with-mdr-tab, warning = FALSE}
summarise_tb_burden(countries = "Russia", 
                    metric = "e_mdr_pct_rr_new", verbose = FALSE,
                    year = 2017, stat = "median") %>% 
  mutate_at(.vars = c("e_mdr_pct_rr_new", "e_mdr_pct_rr_new_lo", "e_mdr_pct_rr_new_hi"),
            funs(ifelse(. > 100, 100, .))) %>% 
  arrange(desc(area)) %>% 
  mutate(`Median percentage of RR* cases with MDR** (95% IQR***)` = 
           pretty_ci(e_mdr_pct_rr_new,
                     e_mdr_pct_rr_new_lo, 
                     e_mdr_pct_rr_new_hi, digits = 1)) %>% 
  mutate(`Median Proportion of RR* cases with MDR** (95% IQR***)` = 
           ifelse(area == "Russian Federation", paste(pretty_round(e_mdr_pct_rr_new), "***"),
                  as.character(`Median percentage of RR* cases with MDR** (95% IQR***)`)
                  )) %>% 
  select(Area = area, `Median percentage of RR* cases with MDR** (95% IQR***)`) %>% 
  knitr::kable(
               caption = "Percentage (\\%) of rifampicin resistant TB cases that have multi-drug resistant TB in Russia and regional medians, with interquartile ranges.",
        booktabs = TRUE) %>% 
  add_footnote(label = c("* Rifampicin resistance", "** Multi-Drug Resistant TB", "*** Interquartile Range"), notation = "none") %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  {.}
```

@@

TB incidence in England and Wales has decreased dramatically from a century ago (Figure \@ref(fig:plot-incidence)^[or see http://www.seabbs.co.uk/shiny/TB_England_Wales for an interactive dashboard]). However, in the past several decades, incidence rates first stabilised and have since increased since their lowest point in the 1990s. In 2000 there were 6044 notified TB cases in England, increasing to a maximum of 8280 notified TB cases in 2011. Since then, notifications have declined year-on-year.[@PHE2016a] Figure \@ref(fig:plot-incidence) includes the interventions discussed above (Table \@ref(tab:tab-interventions)) and indicates that the introduction of several antibiotics and BCG vaccination in the 1950s may have led to an extended decrease in incidence.

### 2019-08-06 rmds/03-getTBinR.Rmd
table formatting

```{r map-tb-incidence-eur, fig.scap = "Map of global TB incidence rates in 2017 as generated by getTBinR.", fig.cap = "Map of global TB incidence rates in 2017 as generated by getTBinR. Visualising the data with a map allows for spatial trends to be rapidly explored.", echo = TRUE, out.extra = ""}
map_tb_burden(metric = "e_inc_100k", verbose = FALSE)
```

>>>>

```{r map-tb-incidence-eur, fig.scap = "Map of global TB incidence rates in 2017 as generated by getTBinR.", fig.cap = "Map of global TB incidence rates in 2017 as generated by getTBinR. Visualising the data with a map allows for spatial trends to be rapidly explored.", echo = TRUE, out.extra = "", fig.height = 4}
map_tb_burden(metric = "e_inc_100k", verbose = FALSE)
```
